\textbf{ Accurate spectrophotometric estimates of luminosity and distance\\ for luminous red-giant stars }

### 2018-07-31 paper/sp.tex
interpretability

>>>>

The linear model we use has many limitations: Linear models are inflexible.
However, they have a great advantage, which is that it is easy to look inside
the model and check whether the dependencies represented there make sense.
One nice thing about the model is that the feature vector $x_n$ for star $n$
contains a set of photometry in magnitudes.
Linear combinations of these photometric measurements are like complex synthetic
magnitudes or colors.
Since the model was trained to deliver luminosities of stars given training data
of different metallicities and extinctions, the synthetic photometry developed
by the model should be, in some sense, metallicity- and extinction-independent
photometry for luminous red-giant stars!
HOGG: CONTINUE THAT THOUGHT.
